---
title: "Mercari EDA"
output: html_notebook
---

```{r}
library(tidyverse)
library(stringr)
```

Load train and create variables for different category levels.

```{r}
train = read_tsv("../../data/train.tsv") %>%
  mutate(category_name_1 = str_match(category_name, "(.*?)/.*")[,2],
         category_name_2 = str_match(category_name, "(.*)/.*")[,2]) %>%  
  rename(category_name_3 = category_name)
```

How many rows?

```{r}
nrow(train)
```

What columns?

```{r}
names(train)
```

Head.

```{r}
head(train)
```

Histogram of item_condition_id

```{r}
plot(hist(train$item_condition_id))
```

# Categories

How many category names?

```{r}
train$category_name_1 %>% unique() %>% length()
```

```{r}
train$category_name_2 %>% unique() %>% length()
```

```{r}
train$category_name_3 %>% unique() %>% length()
```

Distribution of category_name_3?

```{r}
train %>% group_by(category_name_3) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n))
```

```{r}
train %>% group_by(category_name_3) %>% 
  summarise(n = n()) %>% 
  `$`("n") %>% 
  log10() %>% 
  hist(main = "Histogram of log10 number of items in category") %>% 
  plot()
```

Many categories that appear a lot, which should make training on them easier, but many categories that are rare.

How many categories with only one item?

```{r}
train %>% group_by(category_name_3) %>% 
  summarise(n = n()) %>% 
  filter(n == 1)
```

Handmade items can possibly be replaced with identically named items from another broader category.

Items like Home/Furniture/Bathroom Furniture can probably be replaced by other items from Home/Furniture. Is item description any use?

```{r}
train %>% 
  filter(category_name_3 == "Home/Furniture/Bathroom Furniture") %>% 
  `$`("item_description")
```

Probably not - this is a very specific item.

Items like Men/Blazers & Sports Coats/Double Breasted can probably be grouped with other items from Men/Blazers & Sports Coat.
Test dataset.

When fitting initial models with coefficient for each category, should look at correlation between variance/accuracy and number of items in that category.

# Test set

```{r}
test = read_tsv("../../data/test.tsv")%>% 
  mutate(category_name_1 = str_match(category_name, "(.*?)/.*")[,2],
         category_name_2 = str_match(category_name, "(.*)/.*")[,2]) %>% 
  rename(category_name_3 = category_name)
```

Any category_name in test but not train?

```{r}
test$category_name_1 %>% unique() %>% setdiff(train$category_name_1 %>% unique())
```

```{r}
test$category_name_2 %>% unique() %>% setdiff(train$category_name_2 %>% unique())
```

```{r}
test$category_name_3 %>% unique() %>% setdiff(train$category_name_3 %>% unique())
```

So can use category_name_2 for test set when category_name doesn't exist in train.

# Price

price by category_name.

```{r}
train %>% ggplot(aes(x = category_name_2, y = log(price))) +
  geom_point()
```

Lots of price variation within given category_name.

# Other columns

How many items with brand names?

```{r}
sum(!is.na(train$brand_name)) / length(train$brand_name)
```

How many unique brand names?

```{r}
train$brand_name %>% unique() %>% length()
```

Shipping?

```{r}
train$shipping %>% unique()
```

item_description?

```{r}
train$item_description[1:5]
```

Length?

```{r}
item_description_lengths = purrr::map(train$item_description, stringr::str_length) %>% unlist() 
item_description_lengths %>% max(na.rm = TRUE)
```

What is this?

```{r}
train[[which(item_description_lengths == 1046), "item_description"]]
```

List of items with their individual prices.

```{r}
plot(hist(item_description_lengths))
```

Any 0 prices?

```{r}
train %>% 
  filter(price == 0) %>% 
  select(item_description)
```

# Quick modelling

Try predicting price by category_name and item_condition_id.
Not enough memory to use category_name_3 so use category_name_2.
For now, drop category_name NA.

```{r}
model_lm = train %>% 
  filter(!is.na(category_name_3)) %>% 
  lm(log(price + 0.01) ~ category_name_2 + item_condition_id, data = .)
```

```{r}
broom::tidy(model_lm)
```

Large coefficients for items you would expect: tablets, bags, footware etc.

Negative coefficient for item_condition_id, which seems counterintuitive and suggests overfitting.